Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2016-12-15 ms/Accessory/Wenk-Accessory-SI.Rnw
SI: add title, fix table headers

@@

\title{Accessories dominate the costs of producing seed}
\runninghead{C\lowercase{osts of producing seed}}

@@

%\maketitle

@@

\section{A -- Methods for estimating Reproductive allocation}

@@

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
  results <- fit$groupsummary
  acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
  names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
  acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
  acc_slopes
}

@@

names(TableS3) <- c("species","n","r$^2$","p", "n","r$^2$","p")
TableS3[,2] <- format(TableS3[,2],digits=2,nsmall=2)
TableS3[,3] <- format(TableS3[,3],digits=2,nsmall=2)
TableS3[,6] <- format(TableS3[,6],digits=2,nsmall=2)
TableS3[,5] <- format(TableS3[,5],digits=2,nsmall=2)
TableS3[,4] <- format_p(TableS3[,4])
TableS3[,7] <- format_p(TableS3[,7])

TableS3$species  <- paste("\\textit{",unique(TableS3$species),"}", sep="")

print(xtable(TableS3,
               hline.after=c(1),
               align='p{0.1cm}p{4cm}|p{.94cm}p{1cm}p{1.5cm}|p{.75cm}p{1cm}p{1.5cm}',
               caption="Intraspecific correlations between reproductive investment and (a) propagule investment and (b) flower investment"),
               sanitize.text.function=I,
        , table.placement = "H"
        , caption.placement = "top"
        , include.rownames = FALSE
        , include.colnames = TRUE
        , size = "small"
        , floating = FALSE)
@

Table S3.Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as "flower weight (mg) * bud count".

\clearpage
#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
```{r}
xvar <- "repro_inv"
yvar <- "accessory_costs"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

xvar <- "total_weight_0"
yvar <- "accessory_costs"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

xvar <- "age"
yvar <- "accessory_costs"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
mtext(text="age (years)",side=1,line=2,outer=FALSE)
mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
legend_with_r2(results,"topleft")
```

@@

\addcontentsline{toc}{section}{References}
\bibliography{references}

>>>>

% Enable new column type -- centered with fixed
% Following http://texblog.org/2008/05/07/fwd-equal-cell-width-right-and-centre-aligned-content/
\usepackage{array}
\newcolumntype{x}[1]{%
>{\raggedleft}p{#1}}%

@@

\title{Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species}
\runninghead{S\lowercase{hifts in allocation among reproductive tissues}}

@@

\maketitle

@@

\section{A -- Methods for estimating reproductive allocation}

@@

<<echo=FALSE, warning=FALSE>>=

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
  results <- fit$groupsummary
  acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
  names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
  acc_slopes$species <-  paste("\\textit{",species,"}", sep="")
  names(acc_slopes) <- c("species","n","r$^2$","p", "n","r$^2$","p")
  acc_slopes
}

@@

for(i in c(2,3,5,6)){
  TableS3[,i] <- format(TableS3[,i],digits=2,nsmall=2)
}
for(i in c(4,7)){
  TableS3[,i] <- format_p(TableS3[,i])
}
@

\begin{table}[H]
\centering
\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight (mg) $\times$ bud count'}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS3)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\addcontentsline{toc}{section}{B -- References}
\bibliography{references}
